Liveness-Based Garbage Collection

### 2014-07-14 paper/sections/abstract.tex
Still playing with git; modified the abstract slightly

Current garbage collectors  leave much heap-allocated data uncollected
because they preserve data {\em reachable} from a root set.
% However, it is only necessary to preserve {\em live} data---a subset of
% reachable data.
However, only  {\em live} data---a subset of  reachable data---need be
preserved.

Using   a    first-order   functional   language    we   formulate   a
context-sensitive liveness  analysis for structured data  and prove it
correct.   We  then use  a  0-CFA-like  conservative approximation  to
annotate  each  allocation  and  function-call program  point  with  a
finite-state  automaton---which   the  garbage-collector  inspects  to
curtail reachability  during marking. As  a result, fewer  objects are
marked  (albeit  with a  more  expensive  marker)  and then  preserved
(e.g.\ by a copy phase).
% and secondly because of the consequent
%reduced number of collections during a computation.

>>>>

{\color{red}
The memory  requirement of a lazy functional  programming language can
be decreased  in two ways. One can  use the result a  of {\em liveness
analysis}  to preserve only  {\em live}  data---a subset  of reachable
data---during garbage collection. Apart  from evaluated data this will
also  results  in  early  release  of  memory  hogging  closures.   In
addition, one  can also  evaluate closures that  are guaranteed  to be
evaluated in  the future.  The  information that is required  for this
eager evaluation comes from {\em strictness analysis}.
}

Using   a    first-order   functional   language    we   formulate   a
context-sensitive liveness  analysis for structured data  and prove it
correct.   We  then use  a  0-CFA-like  conservative approximation  to
annotate  each  allocation  and  function-call program  point  with  a
finite-state  automaton---which   the  garbage-collector  inspects  to
curtail reachability  during marking. As  a result, fewer  objects are
marked  (albeit  with a  more  expensive  marker)  and then  preserved
(e.g.\ by a copy phase).
